Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-05 SupportingInformation.Rmd
small change

longs<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlongs201117.csv",header=F)
lats<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlats201117.csv",header=F)
longs<-longs[[1]]
lats<-lats[[1]]

df_loc_info_org<-data.frame(loc_no=c(1:length(lats)),longs=longs,lats=lats)
selective_loc<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
df_loc_info<-df_loc_info_org[selective_loc,]
xlim=c(-12,10)
ylim=c(48, 60)

@@

```{r modelsel_and_npa_pns_allsp, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

longs<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlongs201117.csv",header=F)
lats<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlats201117.csv",header=F)
longs<-longs[[1]] 
lats<-lats[[1]]

@@

  temp<-multcall(d_allsp=data_plankton_north_sea,sp=sp,lats=lats,longs=longs,
                                      pfname=paste(resloc2,"/","Sp_",sp,sep=''),good_loc=good_loc)
  stat_plankton_north_sea_allsp[[sp]]<-temp
}
saveRDS(stat_plankton_north_sea_allsp,paste(resloc,file="stat_plankton_north_sea_allsp.RDS",sep=''))

@@

<!--Do the main computations for non-parametric analysis of plankton data-->
```{r stat_plankton_north_sea, echo=F, cache=T, cache=T,  cache.extra=list(seed,data_plankton_north_sea,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

sp<-16
good_loc<-good_loclist(d_allsp=data_plankton_north_sea,sp=sp,data_pt_thrs=45)
longs<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlongs201117.csv",header=F)
lats<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlats201117.csv",header=F)
longs<-longs[[1]] 
lats<-lats[[1]]

stat_plankton_north_sea<-multcall(d_allsp=data_plankton_north_sea,sp=sp,lats=lats,longs=longs,pfname=paste(resloc,"Sp_",sp,sep=''),good_loc=good_loc) 
saveRDS(stat_plankton_north_sea,paste(resloc,file="stat_plankton_north_sea_sp_16.RDS",sep=''))
```

>>>>

longs<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlongs201117.csv",header=F)
lats<-read.csv("./Data/Plankton_North_Sea_data/boxcornerlats201117.csv",header=F)
longs_pns<-longs[[1]]
lats_pns<-lats[[1]]

df_loc_info_org<-data.frame(loc_no=c(1:length(lats_pns)),longs=longs_pns,lats=lats_pns)
selective_loc<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
df_loc_info<-df_loc_info_org[selective_loc,]
xlim=c(-12,10)
ylim=c(48, 60)

@@

```{r modelsel_and_npa_pns_allsp, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,longs_pns,lats_pns,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

@@

  temp<-multcall(d_allsp=data_plankton_north_sea,sp=sp,lats=lats_pns,longs=longs_pns,
                                      pfname=paste(resloc2,"/","Sp_",sp,sep=''),good_loc=good_loc)
  stat_plankton_north_sea_allsp[[sp]]<-temp
}
saveRDS(stat_plankton_north_sea_allsp,paste(resloc,file="stat_plankton_north_sea_allsp.RDS",sep=''))

@@

<!--Do the main computations for non-parametric analysis of plankton data-->
```{r stat_plankton_north_sea, echo=F, cache=T, cache=T,  cache.extra=list(seed,data_plankton_north_sea,longs_pns,lats_pns,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

sp<-16
good_loc<-good_loclist(d_allsp=data_plankton_north_sea,sp=sp,data_pt_thrs=45)

stat_plankton_north_sea<-multcall(d_allsp=data_plankton_north_sea,sp=sp,lats=lats_pns,longs=longs_pns,
                                  pfname=paste(resloc,"Sp_",sp,sep=''),good_loc=good_loc) 
saveRDS(stat_plankton_north_sea,paste(resloc,file="stat_plankton_north_sea_sp_16.RDS",sep=''))
```
